A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Figure~\ref{fig:HiRes_LowRes_Mesh}(a) shows the discretized permeability field for the BaseCase. It has $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements. Figure~\ref{fig:HiRes_LowRes_Mesh}(b) shows the discretized permeability field for the four upscaled models. It has $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$. \red{(STOPPED HERE ...)}

>>>>

Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}. Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs. Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
